Restructuring Data for Exascale Scientific Productivity

### 2016-03-30 papers/2016-Supercomputing/paper.tex
outline

The three broad techniques we study in this paper are bit-based splitting of
double precision floating point data, spatial dimensional sampling of data, and
a temporal interpolation based data prediction technique. In
Section~\ref{details} we provide details on each of these techniques and discuss
the various tradeoffs each technique emobdies. Our evaluation platform presents
a two level storage hierarchy with local SSDs and a remote lustre parallel file
system. Both storage targets have different performance characteristics, and
more details on the evaluation platform are presented in Section~\ref{hardware}.
With this background we present our results in Section~\ref{performance} and
discussion in Section~\ref{res-discussion}. This work is the first step in a
comprehensive new direction for data management at large scale and we discuss
the future of this effort and conclusions in Section~\ref{future}.

@@

The rest of the paper is organized as follows. A brief overview of related work
is presented first in Section~\ref{sec:related}. Section~\ref{sec:end-user}
discusses the programmatic interface end users will see when interacting with
the storage array.
Section~\ref{sec:iof}
briefly discusses the motivation and proposal for the IO forwarding layer.
Section~\ref{sec:iod} describes the IO Dispatcher layer and the broad
functionality it offers.
Section~\ref{sec:daos} discusses how the DAOS
layer functions.
The VOSD layer is discussed in Section~\ref{sec:vosd}.
Next is an exploration of cross-cutting features like transactions and
metadata management in Section~\ref{sec:broader}.
A demonstration of the functionality is presented in
Section~\ref{sec:evaluation}.
The paper is concluded in
Section~\ref{sec:conclusion} with a summary of the broad issues covered in the
paper.

\section{Related Work}
\label{sec:related}

@@

\section{Demonstration}
\label{sec:evaluation}

\section{Conclusions}
\label{sec:conclusion}

The Fast Forward Storage and IO Stack project has designed a good first pass at
addressing the requirements for an extreme scale data storage mechanism.  By
preferring a high level user API like HDF5 rather than using the POSIX
interface, more advanced functionality can be incorporated with less end-user
impact. The introduction of the IOD layer with buffering will absorb the
difference between the compute node IO demands and the available bandwidth in
the storage array. With DAOS supporting translating the container and object
model to the underlying storage options, different storage technologies can be
deployed over time.

With the overall stack design a prototype implementation complete, refinements,
such as fault detection and recovery, can be designed and tested.  These and
other activities for phase 2 will ultimately generate what is likely to be the
next generation storage stack for extreme scale platforms.

>>>>

In the next section, Section~\ref{motivation}, we present the application use
case for our data partitioning approach, and a discussion on the storage
hierarchy in Section~\ref{storage-h}. 
The three broad techniques we study in this paper are bit-based splitting of
double precision floating point data, spatial dimensional sampling of data, and
a temporal interpolation based data prediction technique. 
In
Section~\ref{details} we provide details on each of these techniques and discuss
the various tradeoffs each technique emobdies. Other research efforts and
directions are discussed in Section~\ref{related-work}. 
Our evaluation platform presents
a two level storage hierarchy with local SSDs and a remote lustre parallel file
system. Both storage targets have different performance characteristics, and
more details on the evaluation platform are presented in Section~\ref{hardware}. 
With this background we present our results in Section~\ref{performance} and
discussion in Section~\ref{res-discussion}. This work is the first step in a
comprehensive new direction for data management at large scale and we discuss
the future of this effort and conclusions in Section~\ref{future}.

@@

\section{Motivation and Application Use Cases}
\label{motivation}

\section{Storage Hierarchy}
\label{storage-h}

\section{Partitioning Techniques}
\label{details}

\section{Evaluation Platform}
\label{hardware}

\section{Evaluation}
\label{performance}

\section{Cost-Benefit Discussion}
\label{discussion}

\section{Related Work}
\label{related-work}

@@

\section{Evaluation}
\label{performance}

\section{Future Work and Conclusions}
\label{future}
